Kinematics of the Palomar 5 stellar stream from RR Lyrae stars

### 2019-09-02 paper/main.tex
orcid

% TODO:
% - Check whether I use p > 0.01 or p > 0.1 for sky plot figure
% - Over-plot the sky track borders on MSTO plot
% - Add PM and distance dispersion as parameters to fit, or cite out to the values I fix them to
% - Compute the autocorrelation time for emcee instead, thin by the acor length
%

@@

\shorttitle{RR Lyrae stars in the Pal 5 stream}
\shortauthors{People et al.}
\newcommand{\sa}[1]{{\color{teal} SP: #1}}

@@

\author{Giuliano~Iorio}
\affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}

@@

\author{Vasily~Belokurov}
\affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}

@@

We cross-match the full PS1 RRL catalog with \Gaia~DR2 \citep{Gaia:2018}, using a 1" sky separation tolerance, in order to retrieve astrometric information for these stars.
Although not all PS1 RRLs have been identified as RRLs from \Gaia\ photometry, all of the PS1 RRLs are present in the main point source catalog.
\figurename~\ref{fig:pm} demonstrates that Pal 5 stream members appear in the RRL catalog: This figure shows the \Gaia\ \DR{2} proper motions for all RRLs in the \textcolor{red}{selected} sky window within the distance range $18 < d < 25~\kpc$, then the same for RRLs in a tight selection around the observed stream track (within $1\degr$ of the stream track, \textcolor{red}{see \sectionname~\ref{sec:membership} for details}), and then finally the same for RRLs \emph{excluding} the stream region (excluding stars within $2\degr$ of the stream track).

>>>>

% TODO:
% - Check whether I use p > 0.01 or p > 0.1 for sky plot figure
% - Over-plot the sky track borders on MSTO plot
% - Add PM and distance dispersion as parameters to fit, or cite out to the values I fix them to
% - Compute the autocorrelation time for emcee instead, thin by the acor length

@@

\shorttitle{RR Lyrae stars in the Pal 5 stream}
\shortauthors{Price-Whelan et al.}
\newcommand{\sa}[1]{{\color{teal} SP: #1}}

@@

\author[0000-0003-0293-503X]{Giuliano~Iorio}
\affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}

@@

\author[0000-0002-0038-9584]{Vasily~Belokurov}
\affiliation{Institute of Astronomy, University of Cambridge, Madingley Road, Cambridge CB3 0HA, UK}

@@

We cross-match the full PS1 RRL catalog with \Gaia~DR2 \citep{Gaia:2018}, using a 1" sky separation tolerance, in order to retrieve astrometric information for these stars.
Although not all PS1 RRLs have been identified as RRLs from \Gaia\ photometry, all of the PS1 RRLs are present in the main point source catalog.
\figurename~\ref{fig:pm} demonstrates that Pal 5 stream members appear in the RRL catalog: This figure shows the \Gaia\ \DR{2} proper motions for all RRLs in the selected sky window within the distance range $18 < d < 25~\kpc$, then the same for RRLs in a tight selection around the observed stream track (within $1\degr$ of the stream track, see \sectionname~\ref{sec:membership} for details), and then finally the same for RRLs \emph{excluding} the stream region (excluding stars within $2\degr$ of the stream track).
